\SW Collaboration Publication Policy: CFHT-LS

### 2014-05-14 doc/sw-publication-policy-cfhtls.tex
Further edtis on CFHT-LS policy

\begin{itemize}
% Old versions of this list, which caused a conflict when I (PJM) merged in
% Aprajita's May 2014 edits. Both look out of date to me! Suggested new 
% version is beneath these.
% 
% <<<<<<< HEAD
% \item \sw I: The system paper, describing the project, the interface, the classification analysis methods (SWAP) and results 
% \item \sw II: The \sw  first results including simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis, list of candidates. 
% \item \sw III: Detailed results on candidates from CFHT-LS \textit{including models, follow-up etc}
% \item \sw IV: Detailed comparison and analysis of citizen scientist classification versus lens-finding
% \item \sw X: New lenses(s) in \sw (authored by collaboration members)
%
% =======
% \item \sw I: The system paper, describing the project, the interface, the
% classification analysis methods (SWAP) and results 
% \item \sw II: The \sw  simulations and community performance (not selection
% function), means by which you can compute a selection function for any given
% analysis. 
% \item \sw III: The first new candidates from CFHT-LS \textit{including models,
% follow-up if feasible}
% \item \sw IV: The results from CFHT-LS search including the comparison and
% analysis of citizen scientist classification versus lens-finding algorithms
% (maybe split into smaller papers).
% >>>>>>> 34d2fe73486cc68b301665b1b811cff7804137e8
%
\item \sw I: The system paper, describing the project, the interface & training scheme, the classification analysis methods (SWAP) and results from classification of the training set. (Marshall et al.)
\item \sw II: The \sw CFHTLS project, including description of CFHT-LS specific information (e.g. data/subjects, generation of simulated images), results new lens candidates, and preliminary analysis of \sw compared to previous semi-automatic lens searches in this survey. (More et al.)
\item \sw III: Detailed comparison and analysis of citizen scientist classification versus lens-finding. (More et al.)
%AV to PJM: i thought Anu still wanted the sim-automated serach comparison to be considered in a separate paper
\item \sw IV-X: Detailed results on candidates from CFHT-LS \textit{inclduing lens models, follow-up etc.} (IV: Verma et al. & authored by collaboration members)
\end{itemize}

>>>>

\begin{itemize}
% Old versions of this list, which caused a conflict when I (PJM) merged in
% Aprajita's May 2014 edits. Both look out of date to me! Suggested new 
% version is beneath these.
% 
% <<<<<<< HEAD
% \item \sw I: The system paper, describing the project, the interface, the classification analysis methods (SWAP) and results 
% \item \sw II: The \sw  first results including simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis, list of candidates. 
% \item \sw III: Detailed results on candidates from CFHT-LS \textit{including models, follow-up etc}
% \item \sw IV: Detailed comparison and analysis of citizen scientist classification versus lens-finding
% \item \sw X: New lenses(s) in \sw (authored by collaboration members)
%
% =======
% \item \sw I: The system paper, describing the project, the interface, the
% classification analysis methods (SWAP) and results 
% \item \sw II: The \sw  simulations and community performance (not selection
% function), means by which you can compute a selection function for any given
% analysis. 
% \item \sw III: The first new candidates from CFHT-LS \textit{including models,
% follow-up if feasible}
% \item \sw IV: The results from CFHT-LS search including the comparison and
% analysis of citizen scientist classification versus lens-finding algorithms
% (maybe split into smaller papers).
% >>>>>>> 34d2fe73486cc68b301665b1b811cff7804137e8
%
\item \sw I: The system paper, describing the project, the interface \& training scheme, the classification analysis methods (SWAP) and results from classification of the training set. (Marshall et al.)
\item \sw II: The \sw CFHTLS project, including description of CFHT-LS specific information (e.g. data/subjects, generation of simulated images), results new lens candidates, and preliminary analysis of \sw compared to previous semi-automatic lens searches in this survey. (More et al.)
\item \sw III: Detailed comparison and analysis of citizen scientist classification versus lens-finding. (More et al.)
%AV to PJM: i thought Anu still wanted the sim-automated serach comparison to be considered in a separate paper
\item \sw IV-X: Detailed results on candidates from CFHT-LS \textit{including lens models, follow-up etc.} (IV: Verma et al. \& authored by collaboration members)
\end{itemize}
